\documentclass[12pt,letterpaper,romans]{moderncv}

\moderncvstyle{classic}    
\moderncvcolor{blue}  
\usepackage[scale=0.75]{geometry}

\firstname{Daniel}
\familyname{Salo}
\title{Curriculum Vitae}
\address{604 Massey Ave}{Durham, NC}
\email{dancsalo [at] gmail.com}
\homepage{http://dancsalo.github.io}
\social[github]{dancsalo}

\addtolength{\oddsidemargin}{-.5in}
	\addtolength{\evensidemargin}{-.5in}
	\addtolength{\textwidth}{1.15in}

	\addtolength{\topmargin}{-.5in}
	\addtolength{\textheight}{1.15in}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2016}{M.S. in Engineering}{Duke University, Durham, NC}{}{GPA: 3.80}{Advisor: Dr. Nimmi Ramanujam (BME), Dr. Larry Carin (ECE)}
\cventry{2014}{B.Sc. in Biomedical Engineering}{NC State University, Raleigh, NC}{}{GPA: 3.94}{Bioinstrumentation Concentration. Minor in Piano Performance}

\section{Work Experience}
\cventry{2017 - Pres.}{Data Scientist}{Automated Insights}{Durham, NC}{}{Automated Insights ships Wordsmith, a web application that generates personalized content from data. I am adapting and implementing ML/DL solutions for NLP/NLG applications in Wordsmith.}%

\section{Research Experience}
\cventry{2016 - 2017}{Deep Learning for Object Detection}{Duke University}{Dr. Larry Carin}{}{Creating a semi-supervised, multi-view region-based CNN objection detection algorithm for threat detection in x-ray scans of carry-on luggage in airports. Funded by TSA.}%
\cventry{2014 - 2016}{Optical Diagnostic Device}{Duke University}{Dr. Nimmi Ramanujam}{}{Designed and constructed multispectral LED system for breast margin assessment with spectroscopy with Zemax and Solidworks. Funded by NIH. Decreased scan time by 12\%, weight by 35\%, and power consumption by two orders of magnitude.}%
\cventry{2013 - 2014}{Home Health Monitoring}{NC State University}{Dr. Andrew DiMeo}{}{Invented and produced a wearable device to detect the onset of pulmonary edema in patients with congestive heart failure. Earned first place at joint NC State/UNC Senior Design Competition.}%
\cventry{2013}{Tissue Optics Theory}{Washington University in St. Louis}{Dr. Mikhail Berezin}{}{Programmed NIR instrumentation with VB and Matlab and designed depth penetration experiments as an Amgen Scholar. Published 2 peer-reviewed papers.}%

%\cventry{2012}{The City College of New York}{New York City}{Dr. Lia Krusin}{}{Constructed and programmed a photoelastic spectroscopic ellipsometer as part of a NSF Research Experience for Undergraduates.}%
%\cventry{2011 - 2013}{NC State University}{Raleigh, NC}{Dr. Gregory McCarty}{}{Designed and fabricated cyclic voltammetry nanoprobes for \textit{in vitro} diagnostics.}%
%\cventry{2011}{James G. Cannon Research Center}{Charlotte, NC}{Dr. Ian McKillop}{}{Tested silica drug delivery devices in preclinical liver cancer models for 8 weeks.}%

\section{Scientific Production}
\subsection{Peer-Reviewed Publications}
\cvitem{2016}{Zhang, H., \underline{Salo, D.}, Kim, D. M., \& Berezin, M. Y. (2014). Penetration depth of photons in biological tissues from hyperspectral imaging in shortwave infrared in transmission and reflection geometries. Journal of Biomedical Optics, 21(12), 126006.}
\cvitem{2014}{\underline{Salo, D.}, Kim, D. M., \& Berezin, M. Y. (2014). Multispectral measurement of contrast in tissue-mimicking phantoms in near-infrared spectral range of 650 to 1600 nm spectral range of 650 to 1600 nm. Journal of Biomedical Optics, 19(8), 086008.}


\vspace{0.25cm}


\subsection{Conference Abstracts}
\cvitem{2014}{\underline{Salo, D.}, Kim, D. M., \& Berezin, M. Y. (2014). Wavelength-dependent measurement of contrast in NIR and extended NIR spectral range (650-1600 nm) in phantoms. In Proceedings of SPIE 8940 (Optical Biopsy XII, p. 89400O).}


\vspace{0.25cm}

\subsection{Oral Presentations}
\cventry{2017}{Smiths Detection}{}{Wiesbaden, Hesse, Germany}{}{"Probablistic Neural Networks for Semi-Supervised Learning"}%
\cventry{2015}{Intro. to Finite Element Analysis}{Duke University}{Durham, NC}{}{"Modeling the Efficacy of Photothermal Nanoparticles in the Resection of Urothelial Carcinomas Using Finite Element Methods"}%
\cventry{2014}{Senior Design Symposium}{NC Biotechnology Center}{Durham, NC}{}{"The EdemaBand: An In-Home Monitoring Solution for Patients with Congestive Heart Failure"}%

\cventry{2014}{SPIE Photonics West}{Optical Biopsy XII}{San Francisco, CA}{}{"Wavelength-dependent measurement of contrast in NIR and extended NIR spectral range (650 - 1600nm) in phantoms"}%

\cventry{2013}{Abrams Scholar Symposium}{NC State University}{Raleigh, NC}{}{"An Investigation of Electrode Materials for Abiotic Glucose Fuel Cells"}%

\cventry{2012}{Abrams Scholar Symposium}{NC State University}{Raleigh, NC}{}{"Fabrication of Electroanalytical Chemical Sensors for Application to Neurochemical Disorders"}%

\vspace{0.25cm}

\subsection{Poster Presentations}
\cventry{2016}{GRC Image Science Conference}{Stonehill College}{Easton, MA}{}{"LED Illumination System for the Intraoperative Quantitative Diffuse Reflectance Imaging of Breast Tissue Morphology"}%

\cventry{2014}{Probabilistic Machine Learning}{Duke University}{Durham, NC}{}{"A Multilayer Perceptron for the Differentiation of Fluorescently-Labeled Cervical Cells"}%

\cventry{2013}{Amgen Research Symposium}{Washington University in St. Louis}{MO}{}{"Development of Imaging Instrumentation for the Extended Near Infrared"}

\cventry{2013}{BCMBP Open House}{Washington University in St. Louis}{MO}{}{"Development of Optical Instrumentation in the Extended NIR"}%

\cventry{2012}{REU Research Symposium}{"The City College of New York}{NY}{}{"Phase-Modulated Spectroscopic Ellipsometer Design"}%

\section{Technical Skills}
\cvitemwithcomment{}{\textbf{Programming Languages:}}{\normalfont \begin{flushleft} Python (TensorFlow), Node.js, R, \LaTeX, HTML5, CSS \end{flushleft} }
\cvitemwithcomment{}{\textbf{Machine Learning:}}{\normalfont \begin{flushleft}neural networks, support vector machines, semi-supervised learning, stochastic optimization, clustering \end{flushleft}}
\cvitemwithcomment{}{\textbf{Statistical Methods:}}{\normalfont \begin{flushleft} Bayesian inference, regression models, hierarchical models, hypothesis testing and confidence intervals, dimensionality reduction , non-negative matrix factorization\end{flushleft} }
\cvitemwithcomment{}{\textbf{Software:}}{\normalfont \begin{flushleft} Matlab, Zemax, Solidworks, PCB Artist, ANSYS, Adobe Creative Cloud \end{flushleft} }
\cvitemwithcomment{}{\textbf{Selected Coursework:}}{\normalfont \begin{flushleft}Linear Systems, Digitial Signal Processing, Microcontroller Applications, Signals and Systems, Numerical Linear Algebra, Image and Video Processing, Statistical Optics, Vector Spaces and Applications, Bayesian Statistics, Multivariate Analysis\end{flushleft} }

\section{Accolades}
\subsection{Awards}
\cvitemwithcomment{2016}{NSF GRFP Honorable Mention}{Duke University}
\cvitemwithcomment{2014}{James B. Duke Fellowship}{Duke University}
\cvitemwithcomment{2014}{John T. Chambers Scholar}{Duke University}
\cvitemwithcomment{2014}{1st Place Senior Design Competition}{NC State University, UNC-Chapel Hill}
\cvitemwithcomment{2013}{Amgen Scholar}{Washington University at St. Louis}
\cvitemwithcomment{2013}{Barry Goldwater Nomination}{NC State University}
\cvitemwithcomment{2011}{Caldwell Fellow}{NC State University}
\cvitemwithcomment{2011, 2012}{Abrams Scholar}{NC State University}

\vspace{0.25cm}

\subsection{Honors}
\cvitem{2012}{Phi Kappa Phi}
\cvitem{2012}{NC State Biomedical Engineering Honors Program}
\cvitem{2010}{NC State University Honors Program}

\section{Teaching Assistant}
\cventry{2016}{Intersection of Technology and Women's Health}{BME 210}{Duke University}{}{}%
\cventry{2014}{Analog and Digital Circuits}{BME 290}{NC State University}{}{}%


\section{Outreach}
\cventry{2015 - 2016}{Basketball Coach}{Student U}{Durham, NC}{}{Planning and leading a biweekly basketball clinic after school with 10 - 12 middle school students.}%
\cventry{2015 - 2016}{STEM Tutor}{Student U}{Durham, NC}{}{Meet weekly with two students to prepare for the AP Calculus exam and AP Biology exam.}%
\cventry{2014 - 2015}{FIRST Lego Robotics Coach}{Student U}{Durham, NC}{}{Teaching basic programming and robotic concepts to a year-long team of 12 middle school students twice a week.}%
\cventry{2014}{Science Instructor}{Student U}{Durham, NC}{}{Wrote and gave lessons on elementary physics to a class of 12 public school students in the 8th grade for 6 weeks.}%
\cventry{2013}{Science Camp Counselor}{NC State University}{Raleigh, NC}{}{Coached a group of 8 high school students from underserved counties in North Carolina for a week in a variety of scientific activities.}%
\cventry{2011 - 2013}{Engineering Ambassador}{NC State University}{Raleigh, NC}{}{Gave tours to prospective students and led outreach events at elementary schools with custom-developed curricula.}%

\section{Leadership}
\cventry{2012 - Pres.}{Professional Jazz Pianist}{Self-Employed}{NC}{}{Created a Wordpress site (http://www.jazzpianistnc.com/), performing regularly at weddings and special events, site is top 10 on Google for "jazz pianist nc".}%
\cventry{2015 - 2016}{Duke GradX Talks}{Duke University}{Durham, NC}{}{Served as the Technician. Emceed the event and created the website. }%
\cventry{2015 - 2016}{BME Student Association}{Duke University}{Durham, NC}{}{Served as the Chief Technology Officer. Created a new Wordpress site, designed new logos and graphics with the Adobe Creative Suite, and created a new social media brand for the group.}%
\cventry{2011 - 2014}{The Upstairs Sextet}{NC State University}{Durham, NC}{}{Organized our six-man band through the Music Department as the pianist. Performed at numerous on-campus and off-campus events.}%
\cventry{2011 - 2014}{CRU Fellowship}{NC State University}{Durham, NC}{}{Emceed weekly meetings of 1000 members from stage.}%



\end{document}