\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[left=2.2cm,right=2.2cm,bottom=2.2cm,top=1.5cm]{geometry}
\usepackage{tabularx}
\usepackage{scrextend}

\usepackage{iftex}
\ifPDFTeX
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode.tex}}{}%
\pdfgentounicode=1
\fi

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
	% Header (matching resume look/feel)
	\begin{minipage}[t][1cm][b]{0.5\textwidth}
		\hspace{-\hoffset}\raggedright 
		\Huge \usefont{OT1}{phv}{b}{n} Dan Salo \normalsize
	\end{minipage}
	\begin{minipage}[t][1cm][b]{0.49\textwidth}
		\footnotesize
		\raggedleft Durham, NC \hspace{0.1cm}\textbullet\hspace{0.1cm} (919) 698-2742 \hspace{0.1cm}\textbullet\hspace{0.1cm} \texttt{dancsalo@gmail.com}
	\end{minipage}
	
	\smallskip
	\smallskip
	\smallskip
	
	\small March 10, 2026
	
	\vspace{10pt}
	
	\small
	Hiring Team\\
	10a Labs
	
	\vspace{12pt}
	
	Dear Hiring Team,
	
	\vspace{8pt}
	
	\small
	I’m applying for the Machine Learning Engineer role at 10a Labs because preventing harm from AI systems is the core reason I’ve committed my career to security. As LLMs become more capable and widely deployed, I want to help build the safety and threat-intelligence layer that keeps people and organizations protected in the real world.
	
	\vspace{10pt}
	
	At Proofpoint, I’ve spent years at the intersection of machine learning and adversarial security data, and I’m ready for a new challenge with a sharper safety focus. In my years as a tech lead, I’ve learned how to turn ambiguity into an executable plan for a technical team: define the problem, design a system that can ship, set up evaluation and feedback loops, and iterate until it holds up under production pressure. I'm most proud of our recent work deploying an agentic system for dynamic webpage analysis to complement our sandbox stack.
	
	\vspace{10pt}
	
	I’ve spent years digging into moderation and classifier performance in production, where edge cases and false positives actually matter. Most recently, I've worked extensively on threat detection in dynamic web content and tuning precision/recall tradeoffs that affect users and analysts. Earlier in my career, I led applied ML for Digital Risk content moderation, maintaining a suite of ML and rule-based classifiers across noisy labels, shifting policies, and evolving adversary behavior.
	
	\vspace{10pt}
	
	At 10a Labs, I’d be excited to integrate quickly with teams of engineers and SMEs to measurably improve the classification and moderation of the inputs and outputs of LLM systems of all types. I look forward to hearing from the team.
	
	\vspace{12pt}
	
	Sincerely,\\[10pt]
	\textbf{Dan Salo}
	
\end{document}