%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[resmargin]{resume_style_class} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{setspace}

\topmargin=-0.5in
\oddsidemargin -.4in

\usepackage{fontspec}
\usepackage{hyperref}

\renewcommand{\sectionfont}{\bf\large\fontspec{Fontin}}

\newenvironment{myfont}{\fontspec{Fontin}\selectfont}{\par}
\DeclareTextFontCommand{\textmyfont}{\myfont}

\setlength{\textheight}{10.5in}

\usepackage{tabularx}

\newcommand\textline[3]{%
  \hspace{-\hoffset} \parbox{0.5\textwidth}{\raggedright \Huge \usefont{OT1}{phv}{b}{n} #1 \par \normalsize \normalfont}%
  \parbox{.333\textwidth}{\raggedleft\texttt{#3}}\par\smallskip%
}

\newenvironment{outline}
  {\begin{list}{}{\setlength{\leftmargin}{30pt}\setlength\itemsep{-2pt}}}
  {\end{list}}
  
\newenvironment{outline-cond}
  {\begin{list}{}{
  \setlength{\leftmargin}{30pt}
  \setlength\topsep{-10pt}
  \setlength\itemindent{-30pt}
  }}
  {\end{list}}

\usepackage{array}
\newcolumntype{C}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}[t][1cm][b]{0.3\resumewidth}
\hspace{-\hoffset}\raggedright \Huge \usefont{OT1}{phv}{b}{n} Dan Salo \normalsize
\end{minipage}
\begin{minipage}[t][1cm][b]{0.5\resumewidth}
\footnotesize
\raggedleft \texttt{dancsalo [at] gmail.com} \hspace{0.1cm}\textbullet \hspace{0.1cm} (919) 698-2742 \\ \texttt{\href{https://github.com/dancsalo}{Github}} \hspace{0.1cm}\textbullet \hspace{0.1cm} \texttt{\href{https://www.linkedin.com/in/dancsalo/}{LinkedIn}} \hspace{0.1cm}\textbullet \hspace{0.1cm}  \texttt{\href{https://dancsalo.github.io/about/}{Website}}
\end{minipage}

\smallskip

\moveleft\hoffset\vbox{\hrule width\resumewidth height 2pt}% Horizontal line after name; adjust line thickness by changing the '1pt'



%----------------------------------------------------------------------------------------

\begin{resume}

 
\section{WORK \\ EXPERIENCE}
\begin{large} \textmyfont{Proofpoint} \end{large} \hfill Durham, NC
\vspace{5pt} \\
\textit{Machine Learning Manager and Tech Lead (Apr 2022 - Present)}
\vspace{2pt}
\begin{outline}
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Text-to-SQL}: NL querying of data in the Cloud Protection Platform. Leveraging knowledge distillation and low-rank LMs. Slated for production Q1 2024.
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Form Recognition for DLP}: leading a team of 3 engineers and data scientists. Similarity search algorithm for customer-specific sensitive forms. Slated for production Q4 2023.
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Machine Assisted Triage for ITM}: led a team of 2 engineers. Instance-based anomaly detection algorithm for high-FP insider threat alerts. In prod Q1 2023, precision > 99\%.
\end{outline} 
\textit{Data Scientist (May 2019 - Jul 2021)}, \textit{Senior Data Scientist (Aug 2021 - Mar 2022)}
\vspace{2pt}
\begin{outline}
	\item[$\bullet$\hspace{0.1cm}]  \textmyfont{\href{https://www.proofpoint.com/us/products/archiving-and-compliance/patrol}{Proofpoint Patrol} data science tech lead}: responsible for the maintenance, evaluation, and latency of 54 classifiers across 100's of customers, processing 100k's of social media posts daily. Trained my replacements in 2022.
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Promissory Images Classifier}: designed and delivered an image classification system that detects images that may make a promise of financial gain. Organized an in-house annotation team to acquire labels. Published a \href{https://www.proofpoint.com/us/blog/engineering-insights/development-of-the-promissory-images-classifier}{Proofpoint blog post} and a \href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/11526710}{patent}.
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Physical Locations Classifier}: delivered an NER model to detect mentions of a location with an address. Significant increase in accuracy and latency by replacing BiLSTM-CRF with DistilBERT. Delivered the required 90\% precision. 
	\item[$\bullet$\hspace{0.1cm}]  \textmyfont{NLP Classifier Framework}: ideated and implemented a spaCy-centric framework to serve all classifiers (rules-based and ML). Patented one \href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/11586739}{classifier}.
	% \item[$\bullet$\hspace{0.1cm}]  \textmyfont{Data Science Dashboard}: designed and deployed evaluation dashboards and documentation for all classifiers using Streamlit and Postgres on AWS.
\end{outline} 

\begin{large} \textmyfont{Automated Insights} \end{large} \hfill Durham, NC
\vspace{5pt} \\
\textit{Senior Data Scientist (Dec 2018 - Apr 2019)}, \textit{Data Scientist (Aug 2017 - Nov 2018)}
\vspace{2pt}
\begin{outline}
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Augmented NLG}: Designed and prototyped a natural language generation system as an add-on feature for BI dashboards. Published a  \href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/20220414324}{patent}.
	\item[$\bullet$\hspace{0.1cm}] \textmyfont{Contextual Synonym Suggester}: productionized the custom word vectors (trained using gensim and Common Crawl) with AWS services and Flask and Docker.
\end{outline} 


%\section{PATENTS}
%\begin{outline-cond} 
%	\item  \textmyfont{\href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/20220414324}{Augmented Natural Language Generation Platform}}, Automated Insights, 2019
%	\item  \textmyfont{\href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/11586739}{Method for Identifying Threats From Social Media Content}}, Proofpoint, 2022
%	\item  \textmyfont{\href{https://image-ppubs.uspto.gov/dirsearch-public/print/downloadPdf/11526710}{Systems and Methods For Promissory Image Classification}}, Proofpoint, 2022
%\end{outline-cond} 

\section{TECHNICAL SKILLS}
\begin{outline-cond} 
	\item \textmyfont{Languages}: Python, Bash, Git, SQL, Terraform, Javascript, Go
	\item \textmyfont{Technologies}: PyTorch, TensorFlow, scikit-learn, XGBoost, NumPy, Pandas, spaCy, Docker, OpenCV, MLflow, DVC, Elasticsearch, Postgres, Cassandra, LangChain, AWS stack
	\item \textmyfont{Techniques}: Linear \& Tree-based Models, CNNs, RNNs, GNNs, Transformers, Approximate NN, Clustering, Knowledge Distillation, Semi-Supervised (PU, Weak, Metric)
\end{outline-cond} 

%\section{TEACHING \& MENTORSHIP}
%\begin{outline-cond} 
%\item \textmyfont{BME 521 TA}, Biomedical Electronics at NC State, Spring 2014
%\item \textmyfont{BME 290L TA}, Medtech Device Prototyping Skills at Duke, Spring 2016
%\item \textmyfont{Duke MIDS Capstone Advisor}, Logo Detection at Proofpoint, 2021-2022
%\item \textmyfont{High School Tutor}, Student U, Durham, NC, 2015 - 2017
%\item \textmyfont{FIRST Lego Robotics Coach}, Student U, Durham, NC, 2014 - 2015
%\item \textmyfont{Summer Academy Science Teacher}, Student U, Durham, NC, 2014
%\item \textmyfont{Engineering Ambassador}, NC State, 2011 - 2013  
%\end{outline-cond} 

\section{ACADEMIC ENGAGEMENT}
\begin{outline-cond} 
	\item \textmyfont{Duke MIDS Capstone Advisor}: advised different groups of 3-5 Masters students since 2020. \\Logo Detection (2021), ML Churn Reduction (2022), Low-latency Transformers (2023).
	%\item \textmyfont{Duke Stats Seminar Presenter}: co-presented about \href{https://stat.duke.edu/events/machine-learning-metamorphosis-breaking-models-out-your-local-machine-and-releasing-them}{ML Production} to the Masters program. 
	\item \textmyfont{Washington State University Collaborator}: managing the joint-collaboration with Proofpoint on conformal predictions for binary classifiers.
	\item \textmyfont{Summer Intern Mentor}: managed one undergrad/grad student during summers of 2021-2023.
\end{outline-cond} 





\section{EDUCATION}

\textmyfont{M.S. in Engineering}, Duke University \hfill 2017
\begin{outline}
	\item Abdicated PhD Student
	\item \href{https://bme.duke.edu/faculty/nimmi-ramanujam}{Dr. Nimmi Ramanujam} (BME): Point-of-Care Optical Cancer Imaging
	\item \href{https://scholar.google.com/citations?user=ZhGL6WcAAAAJ&hl=en}{Dr. Larry Carin} (ECE): Deep Learning for Threat Detection in TSA Bag Scans
\end{outline}

\textmyfont{B.Sc. in Biomedical Engineering}, NC State University \hfill 2014
\begin{outline}
	\item Bioinstrumentation Concentration. Minor in Piano Performance.
\end{outline}

%\section{PAPERS}
%\begin{outline-cond}
%	\item \textmyfont{D Salo}, H Zhang, DM Kim, MY Berezin. \textit{Multispectral measurement of contrast in tissue-mimicking phantoms in near-infrared spectral range of 650 to %1600 nm}. Journal of Biomedical Optics, 2014.
%	\item H Zhang, \textmyfont{D Salo}, DM Kim, S Komarov, YC Tai, MY Berezin. \textit{Penetration depth of photons in biological tissues from hyperspectral imaging in shortwave %infrared in transmission and reflection geometries}. Journal of Biomedical Optics, 2015.
%\end{outline-cond}


%----------------------------------------------------------------------------------------
%\section{HONORS}
%Proofpoint Critical Impact Award (2019),
%Automated Insights Hackathon 3rd place (2018),
%NSF GRFP Honorable Mention (2016),
%James B. Duke Fellowship (2014),
%NC State Goldwater Nomination (2013),
%NC State Caldwell Fellow (2010)
\end{resume}
\end{document}