\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[left=2.2cm,right=2.2cm,bottom=2.2cm,top=1.5cm]{geometry}
\usepackage{tabularx}
\usepackage{scrextend}

\usepackage{iftex}

\ifPDFTeX
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode.tex}}{}%
\pdfgentounicode=1
\fi

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]

\newcommand{\resumeEducation}[3]{
    \item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} --- #2 & \textit{#3} \\
	\end{tabular*}
}
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2}
	}
}
\newcommand{\skillsItem}[2]{
	\item\small{
		\textbf{#1}{: #2}
	}
}

\newcommand{\mllibs}[1]{\texttt{\small #1}}

\newcommand{\resumeJobDesc}[1]{
	\vspace{0pt}
	\begin{itemize}[leftmargin=0.4in, itemsep=0pt, topsep=2pt]
		\item \small{#1}
	\end{itemize}
}
\newcommand{\resumeJobWithDate}[3]{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#2} \\
	\end{tabular*}
}

\newcommand{\resumeSubheading}[4]{
    \item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small{#3}} & \textit{\small{#4}} \\
	\end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
	\begin{addmargin}[1em]{0em}
		\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
			\textit{#1} & \textit{\small #2} \\
		\end{tabular*}
	\end{addmargin}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2pt, topsep=3pt]}
	\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeJob}[3]{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
	\end{tabular*}
	\small{#3} 
}

\begin{document}
	
	\begin{minipage}[t][1cm][b]{0.3\textwidth}
		\hspace{-\hoffset}\raggedright \Huge \usefont{OT1}{phv}{b}{n} Dan Salo \normalsize
	\end{minipage}
	\begin{minipage}[t][1.2cm][b]{0.69\textwidth}
		\footnotesize
		\raggedleft
		\texttt{dancsalo [at] gmail.com} \hspace{0.1cm}\textbullet \hspace{0.1cm} (919) 698-2742 \\
		\texttt{\href{https://github.com/dancsalo}{Github}} \hspace{0.1cm}\textbullet \hspace{0.1cm}
		\texttt{\href{https://www.linkedin.com/in/dancsalo/}{LinkedIn}} \hspace{0.1cm}\textbullet \hspace{0.1cm}
		\texttt{\href{https://dancsalo.github.io}{Website}}
		\vspace{1pt}
		\\ Durham, NC, USA
	\end{minipage}
	
	
	\section{Experience}
	\resumeJob{Proofpoint}{}{}
		\vspace{3pt}
	
	\resumeSubSubheading{Staff Machine Learning Scientist}{May 2024 - Present}
	\resumeItemListStart
	\resumeItem{Suspicious Webpage Agent}
	{Technical architect for new AI/ML team in Cork, Ireland. Deployed a browser-use agent with finetuned vision router and novel skills, such as CAPTCHA evasion, to scan 3+ million URLs / day. Built in-house agent framework on top of claude-agents. Coordinating Claude Code best practices across the team. Result: freed up an entire FTE threat analyst from rule-writing. ML Libraries: \mllibs{PyTorch, Huggingface}.}
	
	\resumeItem{URL Defense Oracle}
	{Developed a high-precision, multi-call LLM workflow for detecting evolving URL-based threats. Implemented multi-GPU SFT, CPT pipelines using DeepSpeed for pretraining and knowledge distillation of multimodal QwenVL models and billions of URL-based threat tokens. Seeking reduction in analyst time to complete novel URL-based threat remediation. Langfuse for prompt management and LiteLLM for proxying. ML Libraries: \mllibs{Huggingface}.}
	\resumeItemListEnd
	
	\vspace{4pt}
	
	\resumeSubSubheading{Machine Learning Manager \& Tech Lead}{April 2022 - May 2024}
	\resumeItemListStart
	
	\resumeItem{Training \& Workflow System (ML Platform)}
	{Tech lead for ML training and experimentation workflows using Flyte, MLflow, and Postgres. Built production-grade CLI and artifact management system for reproducible training and tracking. Reduced time-to-production for models from 3 months to 3 weeks and improved observability, cost control.}
	
	\resumeItem{Real-Time Triage System (DLP)}
	{Team of 3 engineers delivering high-throughput ML inference system for SIEM alert triage. Event-driven architecture using AWS Lambdas, Kinesis, and ECS. Saved analysts 2--4 hours per week of manual review, resulting in \$10K+ monthly cost savings. ML Libraries: \mllibs{scikit-learn}.}
	
	\resumeItem{Form Detection Service (DLP)}
	{Tech Lead for the development of a distributed nearest-neighbor computer vision system for custom form detection over batched image data. Built async job runner deployed as a scalable microservice on Kubernetes. ML Libraries: \mllibs{PyTorch, scikit-learn}.}
	
	\resumeItemListEnd
	
	\vspace{4pt}
	
	\resumeSubSubheading{Senior Data Scientist \& Data Scientist}{May 2019 - April 2022}
	\resumeItemListStart
	
	\resumeItem{NLP Classifier System}
	{Designed and operated load-balanced, distributed inference platform on ECS serving 54 NLP classifiers across 1000's of customers classifying 5M+ social media posts/week. Reduced time to remediate customer FPs/FNs from 1 day/week to 2 hours/week with new rule DSL. ML Libraries: \mllibs{spaCy, scikit-learn}.}
	
	\resumeItem{DL Multimodal Classifiers}
	{Built and productionized deep learning text, span, and image classifiers (YOLOv3, DistilBERT). Managed labeling teams for semi-annual retrainings, maintaining 0.8 precision for all classifiers while expanding recall. These features secured \$500K+ in deals with finserv clients. ML Libraries: \mllibs{TensorFlow, PyTorch}.}
	
	\resumeItemListEnd
	
	\resumeJobWithDate{Automated Insights}{July 2017 - May 2019}{}
	\vspace{1pt}
	
	\resumeJobDesc{Lead Data Scientist on two core ML features for \href{https://wordsmith.automatedinsights.com/gallery}{Wordsmith} product of Natural Langauge Generation startup. Created BI dashboard insights recommender system and contextual synonym suggester. ML Libraries: \mllibs{gensim}.}
	
	
	\resumeJobWithDate{Duke University}{August 2014 - June 2017}{}
	\vspace{1pt}
	
	\resumeJobDesc{PhD Student in ML Research Lab under Dr. Larry Carin. Trained object detection model on X-ray scan data for identifying weapons in TSA baggage. Integrated Rapiscan, Smiths Detection scanners. ML Libraries: \mllibs{TensorFlow}.}
	
	\section{Leadership \& Research Impact}
	\resumeSubHeadingListStart
	
	\skillsItem{Organizational Leadership}
	{Co-founded new AI/ML team in Cork, Ireland; hired founding manager and initial team members (2025). Co-authored successful IDA grant proposal on pre-training for cybersecurity models.}
	
	\skillsItem{Hiring \& Talent Development}
	{Directed 2 full hiring processes (junior and staff-level); participated in 12+ additional interview panels across the org. Managed full performance lifecycle for direct reports, including formal improvement plans.}
	
	\skillsItem{Innovation \& External Impact}
	{Named inventor on 3 patents in applied machine learning for cybersecurity: \href{https://dancsalo.github.io/assets/about/patents/patent_aug_nlg.pdf}{Augmented NLG}, \href{https://dancsalo.github.io/assets/about/patents/patent_promissory.pdf}{Promissory Images}, and \href{https://dancsalo.github.io/assets/about/patents/patent_cyberthreats.pdf}{NLP Classifier System}. Placed top 3 in 3 company hackathons. Authored 1 \href{https://www.proofpoint.com/us/blog/engineering-insights/development-of-the-promissory-images-classifier}{technical blog}, delivered multiple external presentations and panel discussions.}
	
	\resumeSubHeadingListEnd

	
	\section{Education}
	\resumeSubHeadingListStart
	
	\resumeEducation
	{M.S., Electrical Engineering}{Duke University}{2014 - 2017}
	
	\resumeEducation
	{B.S., Biomedical Engineering}{North Carolina State University}{2010 - 2014}
	
	\resumeSubHeadingListEnd
	
\end{document}